### 2022-10-26 types.tex
Updates from Overleaf

\documentclass{article}
\usepackage{utf8math,ttquot,mathpartir,amsmath, amssymb, hydrocomments, mathtools,multicol,xspace}
\usepackage[margin=1in]{geometry}
\begin{document}

@@

\newcommand{\closedprogram}{\textit{closed-program}\xspace}
\newcommand{\compiledcomponent}{\textit{compiled-component}\xspace}
\newcommand{\incast}{\textit{incast}\xspace}
\newcommand{\outcast}{\textit{outcast}\xspace}
\newcommand{\seqstart}{\textit{seq-start}\xspace}
\newcommand{\seqend}{\textit{seq-end}\xspace}
\newcommand{\chain}{\textit{chain}\xspace}
\newcommand{\op}{\textit{op}\xspace}
\newcommand{\opt}{τ_{\textit{op}}\xspace}
\newcommand{\N}{ℕ}
\newcommand{\fresh}{\textit{fresh}\xspace}
\newcommand{\inputs}{\textit{inputs}\xspace}
\newcommand{\outputs}{\textit{outputs}\xspace}
\newcommand{\IT}[1]{{\textit{#1}}\xspace}

@@

    {\inferrule{A : in(dₐ'.dₐ''), A : out(dₐ.dₐ''),… ⊢ p
    \\ dₐ' ∈ \{A.dₐ'', dₐ.dₐ''\}
    \\ (A : τₐ,… ⊢ dₐ.dₐ'' : τₐ)…
    }
      {⊢ "declare"~A…~"in"~p}}

    {
      \inferrule[pivot]{|\outputs(\op)| = |p'| \\ 
        C ⊢ p : d \\ C';d.op[0] ⊢ p'}
                {{C,C'} ⊢ [p]\op[p']}}

    {
      \inferrule[inward]{C ⊢ p : d}
                {{C} ⊢ [p]\op : d.\op[0]}}

{
      \inferrule[outward]{|\outputs(\op)| = |p'| \\
        C;d.\op[0] ⊢ p'}
                {{C};d ⊢ \op[p']}}

@@

    \end{mathpar}
  \label{fig:types}
  \caption{Types: top-level}
\end{figure}
\begin{figure}
\begin{mathpar}
    {\inferrule[axoim-transform]{Γ ⊢ d ⇝ d' \\ Γ ⊢ d' : τ}{Γ ⊢ d : τ}}

    {\inferrule[derivation-type-base]{}{Γ ⊢ d : τ}}

@@

>>>>

\documentclass{article}
\usepackage{utf8math,ttquot,mathpartir,amsmath, amssymb, hydrocomments, mathtools,multicol,xspace,stmaryrd }
\usepackage[margin=1in]{geometry}
\begin{document}

@@

\newcommand{\closedprogram}{\textit{closed-program}\xspace}
\newcommand{\compiledcomponent}{\textit{compiled-component}\xspace}
\newcommand{\incast}{\textit{incast}\xspace}
\newcommand{\outcast}{\textit{outcast}\xspace}
\newcommand{\seqstart}{\textit{seq-start}\xspace}
\newcommand{\seqend}{\textit{seq-end}\xspace}
\newcommand{\chain}{\textit{chain}\xspace}
\newcommand{\op}{\textit{op}\xspace}
\newcommand{\opt}{τ_{\textit{op}}\xspace}
\newcommand{\N}{ℕ}
\newcommand{\fresh}{\textit{fresh}\xspace}
\newcommand{\inputs}{\textit{inputs}\xspace}
\newcommand{\outputs}{\textit{outputs}\xspace}
\newcommand{\outarity}{\textit{output-arity}\xspace}
\newcommand{\IT}[1]{{\textit{#1}}\xspace}

@@

    {\inferrule{A : in(dₐ' ▷ dₐ''), A : out(dₐ ▷ dₐ''),… ⊢ p
    \\ dₐ' ∈ \{A ▷ dₐ'', dₐ ▷ dₐ''\}
    \\ (A : τₐ,… ⊢ dₐ ▷ dₐ'' : τₐ)…
    }
      {⊢ "declare"~A…~"in"~p}}

    {
      \inferrule[pivot]{|\outputs(\op)| = |p'| \\ 
        C ⊢ p : d \\ C';d ▷ op[0] ⊢ p'}
                {{C,C'} ⊢ [p]\op[p']}}

    {
      \inferrule[inward]{C ⊢ p : d}
                {{C} ⊢ [p]\op : d ▷ \op[0]}}

{
      \inferrule[outward]{\outarity(\op) = |p'| \\
        C;d ▷ \op[0] ⊢ p'}
                {{C};d ⊢ \op[p']}}

@@

    \end{mathpar}
  \label{fig:types}
  \caption{Types: top-level}
\end{figure}
\begin{figure}
\begin{mathpar}

    {\inferrule[axoim-transform]{Γ ⊢ d ⇝ d' \\ Γ ⊢ d' : τ}{Γ ⊢ d : τ}}

    {\inferrule[parallel]
      {Γ₁ ⊢ p₁ : τ₁ \\ Γ₂ ⊢ p₂ : τ₂}
      {Γ₁,Γ₂ ⊢ (p₁ ∣ p₂) : (τ₁ ∣ τ₂)}}

    {\inferrule[operator-typing]{Γ ⊢ d : τ'}{Γ ⊢ d ▷ \op[n] : (〚\op〛 τ')[n]}}

@@

\inferrule[action-on-type]{}{〚\op〛 τ ≜ τ'}

\inferrule[index-into-type]{}{(τ₁ | … | τ_n | …)[n] ≜ τ_n}

\end{mathpar}
    \caption{Operators: actions on types }
    \label{fig:types2}
\end{figure}
